Adopting agile in the large: motivations, success factors and challenges

### 2014-05-02 journal/article.tex
Lack of resources

>>>>

\subsubsection{Lack of resources}

Lack of resources allocated for supporting the transformation was an evident
problem in many cases. Resources were most often short for training and
coaching, but underbudgeting these activities may be a serious mistake.
Hajjdiab [P20] describes how reluctance of management to invest in training
caused teams to be ill prepared for the agile transformation effort, and
eventually resulted in ending the use of agile methods. As a less dramatic
outcome of shortened training was lower motivation [P45].

Proper coaching was a particular problem for very large organizations. In cases
where the number of teams in need of coaching was large the demand often
exceeded the capacity of available coaches [P1, P6, P23, P49]. Lack of coaching
was also attributed as a reason why the success of pilot teams could not be
repeated when agile was adopted more widely [P9, P45].
Silva and Doss [P47] described that when it was hard to fill the coaching
positions people less seasoned in agile were appointed as coaches, which risked
that agile practices would not be taught correctly.
